Two subtle problems with over-representation analysis

### 2024-07-11 manuscript/manuscript.Rmd
string db

| Tool | Version | Type | Provides FDR values | Provides enrichment score | Proper background handling | Proper FDR | Reference |
| --- | --- | --- | --- | --- | --- | --- | --- |
| DAVID | v2023q4 | Web | Yes | Yes | No | Yes | [@Sherman2022-jn] |
| Panther | v19 | Web | Yes | Yes | Yes | Yes | [@Mi2019-ak] |
| Enrichr | June 2023 | Web | Yes | Yes | Yes | No | [@Kuleshov2016-og] |
| KOBAS-i | KOBAS 3.0 | Web | Yes | No | Yes | No | [@Bu2021-ak] |
| WebGestalt | 2024 | Web | Yes | Yes | No | Yes | [@Elizarraras2024-nr] |
| g:Profiler | Feb 2024 | Web | Yes | No | No | Yes | [@Kolberg2023-nr] |
| STRING-DB | v12.0 | Web | Yes | Yes | ? | ? | [@Szklarczyk2023-an] |
| ShinyGO | v0.80 | Web | Yes | Yes | Yes | Yes | [@Ge2020-lu] |
| Ingenuity Pathway Analysis | ? | ? | ? | ? | ? | ? | [@Kramer2014-kd] |
| BinGO | v3.0.5 | Cytoscape | Yes | No | No | No | [@Maere2005-gq] |
| ClueGO | v2.5.10 | Cytoscape | Yes | No | No | No | [@Bindea2009-jn] |
| clusterProfiler | v4.12.0 | R package | Yes | No | No | No | [@Wu2021-wy] |
| topGO | v2.56.0 | R package | No | No | No | Yes+ | [@Adrian_Alexa2017-nf] |
| GOseq | v1.56.0 | R package | No | No | No* | Yes+ | [@Young2010-iw] |
| goana/kegga | limma v3.60.3 | R package | No | No | No** | Yes+ | [@Ritchie2015-oz] |
| fora | fgsea v1.30.0 | R package | Yes | No | Yes | Yes | [@Korotkevich2016-gd] |

>>>>

| Tool | Version | Type | Provides FDR values | Provides enrichment score | Proper background handling | Proper FDR | Reference |
| --- | --- | --- | --- | --- | --- | --- | --- |
| DAVID | v2023q4 | Web | Yes | Yes | No | Yes | [@Sherman2022-jn] |
| Panther | v19 | Web | Yes | Yes | Yes | Yes | [@Mi2019-ak] |
| Enrichr | June 2023 | Web | Yes | Yes | Yes | No | [@Kuleshov2016-og] |
| KOBAS-i | KOBAS 3.0 | Web | Yes | No | Yes | No | [@Bu2021-ak] |
| WebGestalt | 2024 | Web | Yes | Yes | No | Yes | [@Elizarraras2024-nr] |
| g:Profiler | Feb 2024 | Web | Yes | No | No | Yes | [@Kolberg2023-nr] |
| STRING-DB | v12.0 | Web | Yes | Yes | Yes | Yes | [@Szklarczyk2023-an] |
| ShinyGO | v0.80 | Web | Yes | Yes | Yes | Yes | [@Ge2020-lu] |
| Ingenuity Pathway Analysis | ? | ? | ? | ? | ? | ? | [@Kramer2014-kd] |
| BinGO | v3.0.5 | Cytoscape | Yes | No | No | No | [@Maere2005-gq] |
| ClueGO | v2.5.10 | Cytoscape | Yes | No | No | No | [@Bindea2009-jn] |
| clusterProfiler | v4.12.0 | R package | Yes | No | No | No | [@Wu2021-wy] |
| topGO | v2.56.0 | R package | No | No | No | Yes+ | [@Adrian_Alexa2017-nf] |
| GOseq | v1.56.0 | R package | No | No | No* | Yes+ | [@Young2010-iw] |
| goana/kegga | limma v3.60.3 | R package | No | No | No** | Yes+ | [@Ritchie2015-oz] |
| fora | fgsea v1.30.0 | R package | Yes | No | Yes | Yes | [@Korotkevich2016-gd] |
